Type-Safe Client-Server Communication in Web Applications

### 2014-02-27 paper.tex
Add conclusion section.

Any and all communication between client and server is both strongly typed
and made explicit by the use of the \lstinline!onServer! function, with the
programmer having complete control over the serialization and de-serialization
of data using the appropriate type classes. Aside from the obvious advantages
of type safety, making the crossing of the network boundary explicit helps the
programmer make an informed decision as to when and where server communication
is appropriate.

@@

>>>>

Any and all communication between client and server is both strongly typed
and made explicit by the use of the \lstinline!onServer! function, with the
programmer having complete control over the serialization and de-serialization
of data using the appropriate type classes. Aside from the obvious advantages
of type safety, making the crossing of the network boundary explicit aids the
programmer in making an informed decision as to when and where server
communication is appropriate, as well as helps prevents accidental transmission
of sensitive information intended to stay on the client.

@@

We have presented a programming model which improves on the current state of
the art in client-server web application development. In particular, our
solution combines type safe communication between the client and the server
with purely functional semantics, clear demarcations as to when data is
transmitted and where a particular piece of code is executed, and the ability to
effortlessly share code between the client and the server.

Our model is based on a simple blocking concurrency model rather than explicit
continuations, is well suited for use with a GUI programming style based on
communicating processes with local state, and requires essentially no
modification of existing tools or compilers.
